---
title: "Prediction using Supervised ML"
author: "Nitin Kumar"
date: "10/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##  
In this ,we are predciting the percentage of marks of anstudent based on the number of study hours.
Importing necessary libraries




```{r cars}
#importing libraries
library(tidyverse)
library(dplyr)
library(ggplot2)
library(caTools)
```

Importing required data

```{r }
data_fortask1 <- read.csv("data.csv")
data_fortask1
```

Graphically we will analyse the data.
Scatter plot is used to visualise the linear relationship between the regressor and regressand.
```{r}
scatter.smooth(x = data_fortask1$Hours,y = data_fortask1$Scores,main = 'Scores~Hours')
```
Correlation is a statistical measure that suggests the level of linear independence between two variables.
```{r}
cor(data_fortask1$Scores,data_fortask1$Hours)
```
Now,we will split the dataset into training and test set.
```{r}
# Splitting the dataset into training set and test set
set.seed(120)
split <- sample.split(data_fortask1$Scores,SplitRatio = 0.80)
training_set <- subset(data_fortask1, split == TRUE)
training_set
test_set <- subset(data_fortask1,split == FALSE)
test_set
```
Now we will fit the linear regression model in training set.
```{r}
prediction_fxn <- lm(Scores~Hours,data = training_set)
summary(prediction_fxn)
```

Now we will predict the values of test test.
```{r}
y_prediction <- predict(prediction_fxn,newdata = test_set)
y_prediction
```
Now we will visualise the training set and test set result
```{r}
#Visulaisation of training set result
ggplot()+
  geom_point(aes(x = training_set$Hours,y =training_set$Scores),colour = 'blue')+
  geom_line(aes(x= training_set$Hours, y = predict(prediction_fxn,newdata = training_set)),colour = 'red')+
  ggtitle('Scores vs Hours(training set)')+
  xlab('Hours')+
  ylab('Scores')
#Visulaisation of test set result
ggplot()+
  geom_point(aes(x = test_set$Hours,y =test_set$Scores),colour = 'blue')+
  geom_line(aes(x= test_set$Hours, y = predict(prediction_fxn,newdata = test_set)),colour = 'red')+
  ggtitle('Scores vs Hours(Test set)')+
  xlab('Hours')+
  ylab('Scores')
```

Finally we will predict the score of a student who studies for 9.25 hrs/day.

```{r}
predict(prediction_fxn,data.frame(Hours = 9.25,Scores =""))
```

Score of student who studies for 9.25 hours is 94.51845.
